---
title: "Covid 19 Report"
author: "Chris Annunziato, Anusha Chatterjee, Kelly Zhu, Ifeyinwa Ejisoby-Nwosi" 
date: "`r Sys.Date()`"
output: html_document
---
```{r setup, include = FALSE}
library(tidyverse)
library(knitr)
library(here)
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

```{r}
here::i_am("report.Rmd")
```

```{r table_one, message = FALSE}
here::i_am("report.Rmd")

table_one <- readRDS(file = here::here("output/table_one.RDS"))

table_one

```
The sample is relatively young overall, with a median age around 40 years. Most patients survived (93%), and comorbidities such as diabetes, hypertension, and obesity appear at expected frequencies for a large COVID-19 cohort. These patterns provide useful context for understanding the clinical severity observed later in the analysis.

```{r, pneumonia_plot}
#| fig.align = "center",
#| out.width = "600px"
knitr::include_graphics(
  here::here("output/pneumonia_plot.png"))
```
Patients with pneumonia show a noticeably higher proportion of intubation compared to those without pneumonia. While the non-pneumonia group has a relatively low intubation rate, the pneumonia group has roughly double that proportion. This suggests a strong association between pneumonia and the likelihood of requiring intubation.

```{r,table_two}
pneumonia_table <- readRDS(
  here::here("output/pneumonia_table.rds"))
pneumonia_table
```
The 2×2 table reflects the same pattern seen in the plot: intubation is substantially more common among pneumonia patients. The difference in counts is large enough that it supports the idea of pneumonia being an important clinical predictor of intubation risk.

```{r,logistic}
logistic_table <- readRDS(
  here::here("output/logistic_reg_table.rds"))
logistic_table
```
In the adjusted model, several predictors were significantly associated with mortality. Age shows a small but consistent increase in odds of death, which aligns with expectations for COVID-19 outcomes. Males had higher odds of mortality compared to females. Pneumonia is also strongly associated with increased mortality. The largest effect is seen with intubation; patients who were intubated had substantially higher odds of death. Overall, the model indicates that markers of clinical severity, particularly intubation, are strongly linked to mortality.
